\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Tài liệu tham khảo}

\bibitem{power2002} Daniel J. Power.
\textit{Decision Support Systems: Concepts and Resources for Managers}.
Quorum Books, 2002.

\bibitem{simon1960} Herbert A. Simon.
\textit{The New Science of Management Decision}. Harper \& Brothers, 1960.

\bibitem{crisismmd2018} Firoj Alam, Ferda Ofli, Muhammad Imran.
\textit{CrisisMMD: Multimodal Twitter Datasets from Natural Disasters}. ICWSM, 2018.
\url{https://crisisnlp.qcri.org/crisismmd}

\bibitem{multimodal2020} Ferda Ofli, Firoj Alam, Muhammad Imran.
\textit{Analysis of Social Media Data using Multimodal Deep Learning for Disaster Response}. ISCRAM, 2020.

\bibitem{clip2021} Alec Radford et al.
\textit{Learning Transferable Visual Models From Natural Language Supervision (CLIP)}. ICML, 2021.

\bibitem{salton1988} Gerard Salton and Christopher Buckley.
\textit{Term-weighting approaches in automatic text retrieval}.
Information Processing \& Management, 24(5), 1988.

\bibitem{cortes1995} Corinna Cortes and Vladimir Vapnik.
\textit{Support-vector networks}. Machine Learning, 20, 1995.

\bibitem{breiman2001} Leo Breiman.
\textit{Random Forests}. Machine Learning, 45, 2001.

\bibitem{macqueen1967} J. MacQueen.
\textit{Some Methods for Classification and Analysis of Multivariate Observations}.
Proceedings of the Fifth Berkeley Symposium, 1967.

\bibitem{agrawal1994} Rakesh Agrawal and Ramakrishnan Srikant.
\textit{Fast Algorithms for Mining Association Rules}.
Proceedings of VLDB, 1994.

\bibitem{maaten2008} Laurens van der Maaten and Geoffrey Hinton.
\textit{Visualizing Data using t-SNE}. Journal of Machine Learning Research, 2008.

\bibitem{sklearn} Pedregosa et al. \textit{Scikit-learn: Machine Learning in Python}. JMLR, 2011.

\bibitem{mlxtend} Sebastian Raschka. \textit{MLxtend: Providing machine learning and
data science utilities and extensions to Python's scientific computing stack}. JOSS, 2018.

\bibitem{slides} Slide bài giảng và hướng dẫn bài tập nhóm học phần Hệ hỗ trợ quyết định
do TS. Lê Hải Hà cung cấp, học kỳ 2025.2.
\end{thebibliography}
